4-5-interactive

### 2022-04-17 2-the-cubble-pkg.Rmd
small changes

>>>>

## Why not just use \pkg{dplyr::nest_by}

```{r eval = FALSE}
library(cubble)
library(tidyverse)
left_join(cubble::stations, cubble::climate) %>% 
  dplyr::nest_by(id, lat,  long,  elev, name, wmo_id) %>% 
  tidyr::unnest() %>% 
  group_by(........, geometry)
```

```{r eval = FALSE}
as_cubble(list(spatial = stations, temporal = climate),
          key = id, index = date, coords = c(long, lat))
```

```{r eval = FALSE}
usmap::us_map("states")
```

### 2022-04-17 4-5-interactive.Rmd
clean up bibbib
small changes

---
title: "4-5-interactive"
output: html_document
---
## Interative graphic with cubble

@@

Figure \ref{fig:interactive-popup} shows Figure \ref{fig:interactive-linking} made made with leaflet and popups.

>>>>

---
title: "4-5-interactive"
output: html_document
---
## Interative graphic

@@

Figure \ref{fig:interactive-popup} shows Figure \ref{fig:interactive-linking} made made with leaflet and popups [@leafpop].
